A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-08-07 manuscript.Rmd
Fixed typo

Git and GitHub can do even more to support you when collaborating with fellow researchers, for example, by providing a web interface to track issues and their status (open/closed/resolved) and further means to manage and merge multiple, parallel versions of code (such as branches, pull requests, or merges), but this is beyond the scope of this tutorial. In particular, GitHub's issue management can be leveraged as a post-publication platform to discuss manuscripts and their results [^1].
Another benefit of using Git and GitHub is that experimentation is highly encouraged since you can go back to any state quickly. Even when you lose access to the file on your computer, everything can be backed up on a remote Git server (like GitHub or GitLab). Further, one can reduce the liklihood of dead code accumulating (e.g., lines that have been commented out) because it is safe to simply remove unneeded code blocks and track their removal in Git.

>>>>

Git and GitHub can do even more to support you when collaborating with fellow researchers, for example, by providing a web interface to track issues and their status (open/closed/resolved) and further means to manage and merge multiple, parallel versions of code (such as branches, pull requests, or merges), but this is beyond the scope of this tutorial. In particular, GitHub's issue management can be leveraged as a post-publication platform to discuss manuscripts and their results [^1].
Another benefit of using Git and GitHub is that experimentation is highly encouraged since you can go back to any state quickly. Even when you lose access to the file on your computer, everything can be backed up on a remote Git server (like GitHub or GitLab). Further, one can reduce the likelihood of dead code accumulating (e.g., lines that have been commented out) because it is safe to simply remove unneeded code blocks and track their removal in Git.
